\documentclass[colorlinks,citecolor=blue]{scrartcl}
\author{Sebastian Nordhoff}
\title{Sample document for bibliographies}
\usepackage[
	natbib=true, 
% 	style=nature,
% 	style=science,
	style=biblatex-langsci-unified,	citestyle=langsci-authoryear-comp,
	useprefix = true,
	maxbibnames=99,
	uniquename=false,
	mincrossrefs=99,
	maxcitenames=2,
	isbn=false,
	doi=false,
	url=false,
	eprint=false,
        autolang=hyphen,
	backend=biber,
	indexing=cite
]{biblatex}
\usepackage{hyperref}
\addbibresource{mybib.bib}
\begin{document}
\maketitle 
\section{Bibliographies}
\citet{Chomsky1957} and \citet{Comrie1981} are great books

\citealt{Chomsky1957}

\citet{Chomsky1957}

\citep{Chomsky1957}

\citet[23]{Chomsky1957}

\citep[23]{Chomsky1957}

\citet{Chomsky1957,Comrie1981}

\citeauthor{Chomsky1957} showed in \citeyear{Chomsky1957} ...


\citet{Decker1992,Bashir2003dardic,Bashir2003palula,Liljegren2008,Liljegren2016,Kogan2015} are important works for the Palula language. 

\printbibliography 
\end{document}

# Tasks for class 2-2

----
- Open the sample document `bibtest.tex`
- Locate the commands `\citet` and `\citep`
- Swap the commands and see what happens
- Open the file `bibtest.bib` and familiarise yourself with the structure
- Cite some more entries in `bibtest.tex`
- Create an entry for a book you cite often, an article you cite often, and an entry for your own latest talk. Cite those in `bibtest.tex`

----
- In `bibtest.tex`, change the bibliography style. Try `nature`, and `science`

----
- Create the following outputs: 
    - "Chomsky (1957)"
    - "(Chomsky 1957)
    - "Chomsky (1957: 23)"
    - "(Chomsky 1957: 23)"
    - "(Chomsky 1957, Everett 2000)"
    - "Chomsky showed in 1957 ..."


----
- Visit glottolog.org 
- Choose a language family you like and search it on Glottolog 
- Retrieve 5 bibliographical entries for that language family and paste them into `bibtest.bib`. Cite those entries in the `bibtest.tex`
- Make sure capitalisation is correct in the output

    
----
- remove a comma from the final line of a bib entry. Recompile and see what happens
- remove a `}` from a line in `bibtest.bib`, recompile and see what happens  
- remove the final `}` from a bib entry, recompile and see what happens 
- Create an entry with the title "Under_scores in practices". Cite that entry in `bibtest.tex`. Recompile and see what happens. 
- Create an entry with "$\Theta$-roles in practice". Cite that entry in `bibtest.tex`. Recompile and see what happens. 
- Create an entry with the authors "Juan Pablo Ruiz de Mendoza, John de Ruijter, and Margot van den Berg". Cite that entry. Fix the errors. 

----
- On your local computer, install one of the following programs and open `bibtest.bib` with it:
    - JabRef
    - BibDesk
    - Zotero
    
 https://github.com/langsci/latex4linguists/blob/master/3-1.md   
